Brownian dynamics simulation of cytoplasmic dynein's powerstroke reproduces bidirectional stepping

### 2021-05-23 papers/paper/paper.tex

\section*{TODO August 2020}
\begin{enumerate}
  \item Get new simulations working !!!!!!!!!!!!!!!!!!!
  \item Articulate data we fit to
  \begin{enumerate}
    \item Velocity -> unbinding rate
    \item Ratio of leading vs trailing steps -> exponential parameter
    \item Average step length -> other parameters
    \item Yildiz weird slope -> sticky rate + binding rate
    \item Avoid instant rebinds -> sticky rate
    \item Time to kick from MD??
    \item efficiency (affects instant rebind)
  \end{enumerate}
  \item Do the fit (requires 1 above)
  \item Could have a fixed binding immunity time rather than sticky rate
  \paragraph{Advantages of immunity time}
  \begin{enumerate}
    \item Might accurately reflect a diffusive escape from an energy well
  \end{enumerate}
  \paragraph{Advantages of sticky rate}
  \begin{enumerate}
    \item Accurately reflects the dynamics of a chemical process
  \end{enumerate}
\end{enumerate}

\section*{Plots from MC}
\begin{figure}[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/mc_plots/final_disp_probability_distribution_30.0_5.50e+09_1.00e+09_0.08_1.05_0.0_120.0_197.0_242.0}
\caption{\textbf{Probability distribution plot of final displacement vs. initial displacement.} Dimentions: $nm^{-2}$ (Probability per area of box).}
\label{fig:final_disp_prob}
\end{figure}

\begin{figure}[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/mc_plots/step_length_probability_distribution_30.0_5.50e+09_1.00e+09_0.08_1.05_0.0_120.0_197.0_242.0}
\caption{\textbf{Probability distribution plot of step length vs. initial displacement.} Dimentions: $nm^{-2}$ (Probability per area of box).}
\label{fig:step_length_prob}
\end{figure}

\begin{figure}[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/mc_plots/step_length_1d_probability_density_30.0_5.50e+09_1.00e+09_0.08_1.05_0.0_120.0_197.0_242.0}
\caption{\textbf{Probability density of step lengths.} Dimentions: $nm^{-1}$ (Probability per nm).}
\label{fig:step_length_prob_den}
\end{figure}

\begin{figure}[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/mc_plots/prob_lagging_vs_init_L_-0.3563}
\caption{\textbf{Probability of lagging step vs. initial L.} Dimentions: dimensionless (Probability).}
\label{fig:prob_lagging}
\end{figure}

\begin{figure}[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/mc_plots/ob_time_probability_density_8.0_30.0_5.50e+09_1.00e+09_0.08_1.05_0.0_120.0_197.0_242.0}
\caption{\textbf{Onebounnd Time} Dimentions: $s$.}
\label{fig:ob_time}
\end{figure}

\begin{figure}[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/mc_plots/bb_time_-0.3563}
\caption{\textbf{Bothbound Time.} Dimentions: $s$ .}
\label{fig:bothbound_time}
\end{figure}

@@

>>>>

%\section*{TODO August 2020}
%\begin{enumerate}
%  \item Get new simulations working !!!!!!!!!!!!!!!!!!!
%  \item Articulate data we fit to
%  \begin{enumerate}
%    \item Velocity -> unbinding rate
%    \item Ratio of leading vs trailing steps -> exponential parameter
%    \item Average step length -> other parameters
%    \item Yildiz weird slope -> sticky rate + binding rate
%    \item Avoid instant rebinds -> sticky rate
%    \item Time to kick from MD??
%    \item efficiency (affects instant rebind)
%  \end{enumerate}
%  \item Do the fit (requires 1 above)
%  \item Could have a fixed binding immunity time rather than sticky rate
%  \paragraph{Advantages of immunity time}
%  \begin{enumerate}
%    \item Might accurately reflect a diffusive escape from an energy well
%  \end{enumerate}
%  \paragraph{Advantages of sticky rate}
%  \begin{enumerate}
%    \item Accurately reflects the dynamics of a chemical process
%  \end{enumerate}
%\end{enumerate}

@@

\begin{figure}[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/mc_plots/u_final_disp_probability_distribution_2.0_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
\caption{\textbf{Probability distribution plot of final displacement vs. initial displacement.} Dimentions: $nm^{-2}$ (Probability per area of box).}
\label{fig:final_disp_prob}
\end{figure}

\begin{figure}[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/mc_plots/u_step_length_1d_probability_density_2.0_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
\caption{\textbf{Probability distribution plot of final displacement vs. initial displacement.} Dimentions: $nm^{-2}$ (Probability per area of box).}
\label{fig:final_disp_prob}
\end{figure}

\begin{figure}[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/mc_plots/u_ob_time_probability_density_2.0_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
\caption{\textbf{Probability distribution plot of final displacement vs. initial displacement.} Dimentions: $nm^{-2}$ (Probability per area of box).}
\label{fig:final_disp_prob}
\end{figure}

\begin{figure}[tbhp]
	\centering
	\includegraphics[width=\linewidth]{../../plots/mc_plots/prob_lagging_vs_init_L_-0.5}
	\includegraphics[width=\linewidth]{../../plots/mc_plots/u_trajectory_plot_2.0_5.50e+10_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
	\caption[Fitting Both-bound Parameters]{\textbf{Fitting Both-bound Parameters.} \textit{Top: }Likelihood of a trailing step vs. the initial binding domain distance ($P_{trail.}(L)$ from Equation (\ref{eqn:ProbTrail})). \textit{Bottom: }Trajectory of binding domains over 24 seconds of walking. Experimental data from \cite{Dewitt2012}.}
	\label{fig:BBPlots}
\end{figure}
